---
title: "Scraping Nuclear Reactor"
author: "Kashish Gujral"
Date: "November 9, 2020"
output: html_notebook
---
```{r}
#load packages
library(rvest)
library(lubridate)
library(dplyr)
library(DataComputing)
```

```{r}
page <- "http://en.wikipedia.org/wiki/List_of_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

head(tableList[[22]])
```
# Your Turn 1
#### Q - In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?
#### A - The table is not tidy. There are variables that are repeating themselves and that doesn't make a tody table. A tidy table would have a row with no variables repeating and have columns with similar data in them.

```{r}
names(Japan)[c(3,7)] <- c("type", "grossMW")

Japan <- Japan %>%
  filter(row_number() > 1) %>%
  rename(name = Name, 
         reactor = `UnitNo.`,
         model = Reactor,
         status = Status, 
         netMW = `Capacity in MW`,
         construction = `Construction start`,
         operation = `Commercial operation`, 
         closure = Closure) %>%
  mutate(netMW = as.numeric(netMW), grossMW = as.numeric(grossMW)) %>%
  mutate(construction = dmy(construction), operation = dmy(operation), 
         closure =dmy(closure))

# Inspect Result
head(Japan)
str(Japan)
```
# Your Turn 2
#### Most of the nuclear reactors use BWR - Boiling water reactor and PWR - Pressurized water reactor
```{r}
Japan %>%
  ggplot(aes(y = netMW, x = construction)) + geom_point(aes(color = type))
```

# Your Turn 3
```{r}
China <- tableList[[10]]
names(China)[c(3,7)] <- c("type", "grossMW")

China <- China %>%
  filter(row_number() > 1) %>%
  rename(name = Name, 
         reactor = `UnitNo.`,
         model = Reactor,
         status = Status, 
         netMW = `Capacity in MW`,
         construction = `Construction start`,
         operation = `Commercial operation`, 
         closure = Closure) %>%
  mutate(netMW = as.numeric(netMW), grossMW = as.numeric(grossMW)) %>%
  mutate(construction = dmy(construction), operation = dmy(operation), 
         closure =dmy(closure))

# Inspect Result
head(China)
str(China)
```
```{r}
Japan <- Japan %>%
  mutate(country = "Japan") # make a new variable called "country" for Japan data

China <- China %>%
  mutate(closure = ymd(closure),# convert this variable to a date format for China data
  country = "China")# make a new variable called "country" for China data

China_Japan <- rbind(China, Japan)
```

# Your Turn 4
```{r}
names(Italy)[c(3,7)] <- c("type", "grossMW")

Italy <- Italy %>%
  filter(row_number() > 1) %>%
  rename(name = Name, 
         reactor = `UnitNo.`,
         model = Reactor,
         status = Status, 
         netMW = `Capacity in MW`,
         construction = `Construction start`,
         operation = `Commercial operation`, 
         closure = Closure) %>%
  mutate(netMW = as.numeric(netMW), grossMW = as.numeric(grossMW)) %>%
  mutate(construction = dmy(construction), operation = dmy(operation), 
         closure =dmy(closure))

# Inspect Result
head(Italy)
str(Italy)


```

```{r}

Italy %>%
  mutate(name_reactor = paste(name, reactor)) %>%
  ggplot(aes(y = name_reactor, x = operation, size = 4)) +
  geom_segment(aes(y = name_reactor, yend = name_reactor, 
                   x = construction, xend = operation, color = type)) +
  geom_point(aes(y = name_reactor, x = closure, shape = status))
```

